Topological order in the quantum dimer-pentamer model

### 2015-09-04 qdpm_paper.tex
Started formatting paper

\documentclass[aps,floatfix,11pt,twocolumn]{revtex4-1}
\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

    It became apparent in the 80's and early 90's that the Landau theory of symmetry breaking did not
    encompass all possible types of order that can be found in the groundstate of a condensed matter system. 
    In fact it was found that the symmetry of a system
    could increase as a system was cooled past a critical tempature and a phase transition occured
    that did not fit into Landau's theory. In these cases the odering 
    that could not be described with an order
    parameters \cite{wen_1990} was a topological order. Though the discovery of topological order was originally thought
    to help understand superconductivity in the context of chiral spin systems \cite{HERE} it was
    not able to do so. However, due to the robust ground state degeneracy of systems exhibiting
    topological order they have become candidates for methods of storing and manipulating
    quantum information.  Also important to the field of quantum information, but interesting in
    its own right, is that topologically ordered systems exhibit fractal excitations.

@@

>>>>

\documentclass[twocolumn,prb,aps,floatfix,superscriptaddress]{revtex4-1}

\usepackage{bm}%bold math
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{scalerel}
\epstopdfsetup{update} % only regenerate pdf files when eps file is newer
\linespread{1}
\usepackage[export]{adjustbox}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Topological order in the quantum dimer-pentamer model}

\author{Owen Myers}
\email{omyers@uvm.edu}
\affiliation{Department of Physics, University of Vermont, Burlington, VT 05405, USA}

\author{C. M. Herdman}
\affiliation{Institute for Quantum Computing, University of Waterloo, Ontario, N2L 3G1, Canada}
\affiliation{Department of Physics \& Astronomy, University of Waterloo, Ontario, N2L 3G1, Canada}
\affiliation{Department of Chemistry,  University of Waterloo, Ontario, N2L 3G1, Canada}

\begin{abstract}

\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

    It became apparent in the 80's and early 90's that the Landau theory of symmetry breaking did not
    encompass all possible types of order that can be found in the groundstate of a condensed matter system. 
    In fact it was found that the symmetry of a system
    could increase as a system was cooled past a critical tempature and a phase transition occured
    that did not fit into Landau's theory. In these cases the odering 
    that could not be described with an order
    parameters~\cite{Wen1990} was a topological order. Though the discovery of topological order was originally thought
    to help understand superconductivity in the context of chiral spin systems \cite{HERE} it was
    not able to do so. However, due to the robust ground state degeneracy of systems exhibiting
    topological order they have become candidates for methods of storing and manipulating
    quantum information.  Also important to the field of quantum information, but interesting in
    its own right, is that topologically ordered systems exhibit fractal excitations.

@@

\bibliographystyle{apsrev4-1}
\bibliography{QDPM}
